Fusion Moves for Correlation Clustering

### 2014-11-14 paper/egpaper_for_review.tex
fixed stuff

\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each fusion move can be interpreted as an optimization of an inner polytope.
Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optimum. When optimizing over the blue polytope we stay in $y_1$ as optimum,
when optimizing over the green polytope we find $y_2$ which we will never leave again. 
}
\label{fig:polyheadral}
\end{figure}

>>>>

\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each fusion move can be interpreted as an optimization of an inner polytope.
Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optimum. Finally, when optimizing over the blue polytope we stay in $y_1$ as optimum,
when optimizing over the green polytope we find $y_2$ which we will never leave again. 
}
\label{fig:polyheadral}
\end{figure}

### 2014-11-14 paper/inputs/fig_hc_alg.tex
proofs
fixed stuff

\begin{center}
\begin{figure}
\begin{center}
\resizebox{0.75\linewidth}{!}{
%\resizebox{!}{0.25\linewidth}{%
    \begin{tikzpicture}
    %\draw (0,-1)node (dummyLow){} ;
    %\draw (0, 3)node (dummyLow){} ;
    \draw (2,2) node[nS] (n0) {$0$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (2,0) node[nS] (n3) {$3$}; 
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

@@

}
\caption{
    Hierarchical clustering can be used to optimize
    Eq.~\ref{eq:edgeproblem}.
    In each step, the two nodes connected via the edge with 
    the highest weight are merged by contracting this edge.
    (to be contracted edge is shown in green).
    Due to edge contraction parallel edges can occur which 
    are merged into single ones, and their weights are summed up.
    The algorithm stops when the highest edge weight is smaller
    or equal to zero (edge shown in blue).
}\label{fig:hc_alg}
\end{center}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}[t]
\begin{center}
\resizebox{0.75\linewidth}{!}{
%\resizebox{!}{0.25\linewidth}{%
    \begin{tikzpicture}
    %\draw (0,-1)node (dummyLow){} ;
    %\draw (0, 3)node (dummyLow){} ;
    \draw (2,2) node[nS] (n0) {$0$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (2,0) node[nS] (n3) {$3$}; 
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

@@

}
\caption{
    Energy-based Hierarchical clustering can be used to greedily optimize
    Eq.~\ref{eq:edgeproblem}.
    In each step, the two nodes connected via the edge with 
    the highest weight are merged by contracting this edge.
    (edge to be contracted is shown in green).
    Due to edge contraction parallel edges can occur, which 
    are merged into single ones, and their weights are summed up.
    The algorithm terminates when the highest edge weight is smaller
    or equal to zero (edge shown in blue).
}\label{fig:hc_alg}
\end{center}
\end{figure}
\end{center}

### 2014-11-14 paper/introduction-new.tex
fixed stuff

\vspace{0.1cm}
\noindent \textbf{Outline:} 
In Sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition and introduce 
the correlation clustering objective.
Next we give a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
We evaluate the proposed methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.

@@

\input{inputs/fig_notation.tex}
\section{Notation and Problem Formulation}\label{sec:problem_formulation}
Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
%
The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
We will use $w_e$ as a shorthand for $w(e)$.
A positive weight expresses the desire that two adjacent nodes should
be merged, whereas a negative weight indicates
that these nodes should be separated into two different regions.
%
%A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
%of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
%
%\input{inputs/fig_notation.tex}
A segmentation of the graph $G$ can be either given by a
node labeling $l \in \mathbb{N}^{|V|}$
or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation}.
An edge labeling is only consistent if it does not violate any cycle constraint~\cite{kappes_2013_arxiv}.
We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.
%
By $l(y)$ we denote a node labeling for a segmentation given by $y$.

Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
of the edges between distinct segments is minimized. This can be formulated in the node domain
by assigning each node $i$ a label $l_i \in \mathbb{N}$
\begin{align}
  l^* &= \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
\end{align} 
or in the edge domain, by labeling each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
\begin{align}
  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}.%\\ 
\end{align}
As shown in~\cite{kappes_2013_arxiv}  both problems are equivalent, but formulation \ref{eq:nodeproblem}
suffers from ambiguities in the formulation, \cf Fig.~\ref{fig:notation}.

>>>>

\vspace{0.1cm}
\noindent \textbf{Outline:} 
In Sec.~\ref{sec:problem_formulation} we give a 
detailed problem definition and introduce 
the correlation clustering objective.
Next we give a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
We evaluate the proposed methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.

@@

\input{inputs/fig_notation.tex}
\section{Notation and Problem Formulation}\label{sec:problem_formulation}
Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
%
The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
We will use $w_e$ as a shorthand for $w(e)$.
A positive weight expresses the desire that two adjacent nodes should
be merged, whereas a negative weight indicates
that these nodes should be separated into two distinct regions.
%
%A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
%of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
%
%\input{inputs/fig_notation.tex}
A segmentation of the graph $G$ can be either given by a
node labeling $l \in \mathbb{N}^{|V|}$
or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation}.
An edge labeling is only consistent if it does not violate any cycle constraint~\cite{kappes_2013_arxiv}.
We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.
%
By $l(y)$ we denote some node labeling for a segmentation given by $y$.

Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
of the edges between distinct segments is minimized. This can be formulated in the node domain
by assigning each node $i$ a label $l_i \in \mathbb{N}$
\begin{align}
  l^* &= \argmin_{l \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
\end{align} 
or in the edge domain, by labeling each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
\begin{align}
  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}.%\\ 
\end{align}
As shown in~\cite{kappes_2013_arxiv}  both problems are equivalent, but formulation \ref{eq:nodeproblem}
suffers from ambiguities in the representation, \cf Fig.~\ref{fig:notation}.
